initial_analysis_notebook

### 2021-04-27 exploratory/notebook/initial_analysis/initial_analysis_notebook.Rmd
plot histology/toxin by moribund not mild/moderate/severe

histology %>% 
  left_join(distinct(select(metadata, mouse_id, early_euth)), by = 'mouse_id') %>% 
  filter(!is.na(early_euth)) %>% 
  mutate(early_euth = ifelse(early_euth, 'Moribund', 'Colonized'),
         mouse_id = paste0(cage_id, '_', ear_tag)) %>% 
  inner_join(mouse_by_outcome, by = c('mouse_id')) %>%
  pivot_longer(cols = c(edema_tissue, inflammation_tissue, epithelial_damage, summary_score),
               names_to = 'histology', values_to = 'score') %>% 
  ggplot(aes(x = histology, y = score, color = outcome)) +
    stat_summary(fun.data = 'median_hilow', fun.args = (conf.int=0.5), position = position_dodge(width = 0.4)) +
    #geom_boxplot() + 
    #geom_point(position = position_jitterdodge(), alpha = 0.5) + 
    theme_bw() + 
    labs(x = NULL, y = 'Histology Score', fill = 'Outcome') +
    scale_x_discrete(guide = guide_axis(angle = 45)) + 
    facet_grid(.~early_euth)
```

@@

```{r toxin}
toxin %>% 
  inner_join(select(metadata, group, human_source), by = c('group')) %>% 
  left_join(mouse_by_outcome, by = c('human_source')) %>% 
  filter(!is.na(outcome)) %>% 
  mutate(day = as.numeric(toxin_sample_day)) %>% 
  ggplot(aes(x = day, y = Log_repiricoal_dilution, color = outcome)) + 
#    geom_line(aes(color = outcome, group = mouse_id)) + 
    stat_summary(fun.data = 'median_hilow', fun.args = (conf.int=0.5), position = position_dodge(width = 0.4)) +
    labs(x = 'Day', y = 'Toxin activity') + 
#    facet_grid(outcome~.) + 
    theme_bw()
```

>>>>

histology %>% 
  left_join(distinct(select(metadata, mouse_id, early_euth)), by = 'mouse_id') %>% 
  filter(!is.na(early_euth)) %>% 
  mutate(early_euth = ifelse(early_euth, 'Moribund', 'Colonized'),
         mouse_id = paste0(cage_id, '_', ear_tag)) %>% 
  inner_join(mouse_by_outcome, by = c('mouse_id')) %>%
  pivot_longer(cols = c(edema_tissue, inflammation_tissue, epithelial_damage, summary_score),
               names_to = 'histology', values_to = 'score') %>% 
  ggplot(aes(x = early_euth, y = score, , color = early_euth, fill = early_euth)) +
    #stat_summary(fun.data = 'median_hilow', fun.args = (conf.int=0.5), position = position_dodge(width = 0.4)) +
    geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
    #geom_point(position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5) + 
    theme_bw() + 
    labs(x = NULL, y = 'Histology Score', fill = 'Outcome') +
    scale_x_discrete(guide = guide_axis(angle = 45)) + 
    facet_grid(.~histology) + 
    guides(color = 'none') + 
    theme(legend.position = 'bottom')
```

@@

```{r toxin}
toxin %>% 
  inner_join(select(metadata, group, human_source), by = c('group')) %>% 
  left_join(mouse_by_outcome, by = c('human_source')) %>% 
  filter(!is.na(outcome)) %>% 
  mutate(day = as.numeric(toxin_sample_day),
         outcome = ifelse(outcome == 'moribund', as.character(outcome), 'colonized')) %>% 
  ggplot(aes(x = outcome, y = Log_repiricoal_dilution, fill = outcome, color = outcome)) + 
    stat_summary(fun.data = 'median_hilow', fun.args = (conf.int=0.5), position = position_dodge(width = 0.4)) +
    geom_jitter(width= 0.3, height = 0, alpha = 0.3) + 
    labs(x = 'Day', y = 'Toxin activity') + 
    facet_grid(.~day) + 
    theme_bw() +
    theme(legend.position = 'bottom')
```
